### 2017-12-11 UOW_thesis_template_v2-0/thesis_template/chapters/jumpImpVol.tex
:art: More changes from Monday 11 Dec

\subsection{Homogeneity of the solution}
First, we assume that the payoff function $\phi$ now depends on a parameter~$x' > 0$ (i.e., $\phi = \phi(x;x')$).  The motivation for this is that in the case of a European put or call, $x'$ represents the strike price. Furthermore, we assume that $\phi$ is homogeneous of degree one in~$x$ and $x'$. That is, we assume
$$
	\phi(\beta x; \beta x') = \beta \phi(x;x').
$$ 
Note that standard put and call payoffs satisfy this assumption. We show that the option price function~$v$ is homogeneous of degree one in~$x$ and $x'$. That is, we want to show for $v = v(x,t; x')$ that
		\begin{equation}
			\label{eqn:homogen}
			v(\beta x, t; \beta x') = \beta v(x,t; x')
		\end{equation}
for all $\beta > 0$. This equality can be proven via a uniqueness argument as follows. We first express \eqref{eqn:PIDE} as $\mathscr{L} v = 0$. Now let $w = w(x,t; x')$ solve the following final value problem:
		\begin{align}
			\label{eqn:subPIDE}
			\begin{split}
			&\mathscr{L}w = 0, \qquad w(x,T; x') = \beta\phi(x;x').
			\end{split}
		\end{align}
Next, we define the function $v_1(x,t;x') = \beta v(x,t;x')$, where $v$ is a solution to (\ref{eqn:PIDE}), (\ref{eqn:PIDEcondition}). Then
	\begin{align*}
		\mathscr{L}v_1 = \beta \mathscr{L}v = 0.
	\end{align*}
For the terminal condition, since $v(x,T;x') = \phi(x;x')$, this implies that
	\begin{equation*}
		v_1(x,T;x') = \beta v(x,T; x') = \beta\phi(x;x').
	\end{equation*}
Therefore $v_1$ satisfies the final value problem \eqref{eqn:subPIDE}. On the other hand, we now let $v_2(x,t,x') = v(\beta x, t; \beta x')$. Computing the derivatives gives
	\begin{equation*}
		\fr{\pr v_2}{\pr x} = \beta D_1v, \quad \fr{\pr^2 v_2}{\pr x^2} = \beta^2 D_{11}v,
	\end{equation*}
where $D_1$ and $D_{11}$ represent the first and second partial derivatives with respect to the first argument, respectively. Substituting these into (\ref{eqn:subPIDE}), we get
	\begin{align*}
		\mathscr{L}v_2 = \mathscr{L}v = 0,
	\end{align*}
and by the homogeneity of $\phi$, the terminal condition is
	\begin{align*}
		v_2(x,T;x') = v\left( \beta x, T; \beta x' \right) = \phi(\beta x; \beta x') = \beta \phi(x;x').
	\end{align*}
Hence $v_2$ also satisfies the final value problem \eqref{eqn:subPIDE}. By uniqueness, we have
	\begin{equation*}
		v\left(\beta x, t; \beta x'\right) = v_2(x,t;x') = v_1(x,t;x') = \beta v(x,t;x'),
	\end{equation*}
thus proving the homogeneity property for $v$ and any general payoff $\phi$ that is homogeneous of degree one in~$x$ and $x'$.

\subsection{Derivation of a Dupire-like PIDE via Euler's theorem on homogeneous functions}
The partial derivatives of the Dupire equation~\cite{Gatheral2006} are with respect to the strike price $K$. Thus to derive a Dupire-like PIDE, we will require partial derivatives in terms of $x'$ (the analogous variable for $K$). This can be done by invoking Euler's theorem for homogeneous functions~\cite[pp. 317]{Kishan2007} to $v$ and we get
	\begin{equation*}
		x\fr{\pr v}{\pr x} + x'\fr{\pr v}{\pr x'} = v,
	\end{equation*}
since $v$ has been shown to be homogeneous in $x$ and $x'$ of degree one. By differentiating the above equation with respect to $x$ and $x'$, we obtain
	\begin{equation*}
		x\fr{\pr^2 v}{\pr x^2} = -x'\fr{\pr^2 v}{\pr x \pr x'}, \quad x'\fr{\pr^2 v}{\pr x'^2} = -x\fr{\pr^2 v}{\pr x' \pr x},
	\end{equation*}
respectively. Hence it follows that
	\begin{equation*}
		x^2\fr{\pr^2 v}{\pr x^2} = x'^2\fr{\pr^2 v}{\pr x'^2}.
	\end{equation*}
The only term left to account for is the integral in (\ref{eqn:PIDE}). Notice that the first integrand term depends on~$y$; we want to transfer the dependency on $y$ to the third argument (i.e., $x'$). This can be achieved by the homogeneity property in (\ref{eqn:homogen}), and we obtain
	\begin{align*}
		v(xy,t; x') &= v\left(xy,t;\fr{x'y}{y}\right) = yv\left( x,t;\fr{x'}{y} \right).
	\end{align*}
Thus, setting $u(x',t; x) = v(x',t; x)$ and replacing all the $x$ derivatives with $x'$ derivatives and substituting the above rearrangement for the integrand, we get
	\begin{align}
		\label{eqn:DupireLike}
		\begin{split}
		\fr{\pr u}{\pr t} &- (q(t) + \kappa\lambda)u - (r(t) - q(t) - \kappa\lambda)x'\fr{\pr u}{\pr x'} + \fr{1}{2}\sigma(t)^2x'^2\fr{\pr^2 u}{\pr x'^2} \\
		& {} + \lambda \int_0^\infty \left( yu\left( \fr{x'}{y},t; x \right) - u(x',t; x) \right)f(y) \, \d y = 0
		\end{split}
	\end{align}
with
	\begin{equation}
		\label{eqn:DupireCond}
		u(x',T; x) = \phi(x';x),
	\end{equation}
since $u$ now depends on the variables $x'$ and $t$ with $x$ as a parameter. Equations~(\ref{eqn:DupireLike}) and (\ref{eqn:DupireCond}) together form the Dupire-like PIDE system for options in a jump-diffusion framework. Note that this reduces to the standard Dupire PDE as seen in \cite{Gatheral2006} in the absence of jumps (i.e., $\lambda = 0$) when $\phi$ is either the call or put payoff.

>>>>

\subsection{Homogeneity of the solution}
First, we assume that the payoff function $\phi$ now depends on a parameter~$x' > 0$ (i.e., $\phi = \phi(x;x')$).  The motivation for this is that in the case of a European put or call, $x'$ represents the strike price. Furthermore, we assume that $\phi$ is homogeneous of degree one in~$x$ and $x'$. \textcolor{blue}{That is, we assume
$$
	\phi(\beta x; \beta x') = \beta \phi(x;x').
$$}
Note that standard put and call payoffs satisfy this assumption. We show that the option price function~$v$ is homogeneous of degree one in~$x$ and $x'$. That is, we want to show for $v = v(x,t; x')$ that
		\begin{equation}
			\label{eqn:homogen}
			v(\beta x, t; \beta x') = \beta v(x,t; x')
		\end{equation}
for all $\beta > 0$. This equality can be proven via a uniqueness argument as follows. We first express \eqref{eqn:PIDE} as $\mathscr{L} v = 0$. Now let $w = w(x,t; x')$ solve the following final value problem:
		\begin{align}
			\label{eqn:subPIDE}
			\begin{split}
			&\mathscr{L}w = 0, \qquad w(x,T; x') = \beta\phi(x;x').
			\end{split}
		\end{align}
Next, we define the function $v_1(x,t;x') = \beta v(x,t;x')$, where $v$ is a solution to (\ref{eqn:PIDE}), (\ref{eqn:PIDEcondition}). Then
	\begin{align*}
		\mathscr{L}v_1 = \beta \mathscr{L}v = 0.
	\end{align*}
For the terminal condition, since $v(x,T;x') = \phi(x;x')$, this implies that
	\begin{equation*}
		v_1(x,T;x') = \beta v(x,T; x') = \beta\phi(x;x').
	\end{equation*}
Therefore $v_1$ satisfies the final value problem \eqref{eqn:subPIDE}. On the other hand, we now let $v_2(x,t,x') = v(\beta x, t; \beta x')$. Computing the derivatives gives
	\begin{equation*}
		\fr{\pr v_2}{\pr x} = \beta D_1v, \quad \fr{\pr^2 v_2}{\pr x^2} = \beta^2 D_{11}v,
	\end{equation*}
where $D_1$ and $D_{11}$ represent the first and second partial derivatives with respect to the first argument, respectively. Substituting these into (\ref{eqn:subPIDE}), we get
	\begin{align*}
		\mathscr{L}v_2 = \mathscr{L}v = 0,
	\end{align*}
and by the homogeneity of $\phi$, the terminal condition is
	\begin{align*}
		v_2(x,T;x') = v\left( \beta x, T; \beta x' \right) = \phi(\beta x; \beta x') = \beta \phi(x;x').
	\end{align*}
Hence $v_2$ also satisfies the final value problem \eqref{eqn:subPIDE}. By uniqueness, we have
	\begin{equation*}
		v\left(\beta x, t; \beta x'\right) = v_2(x,t;x') = v_1(x,t;x') = \beta v(x,t;x'),
	\end{equation*}
thus proving the homogeneity property for $v$ and any general payoff $\phi$ that is homogeneous of degree one in~$x$ and $x'$.

\subsection{Derivation of a Dupire-like PIDE via Euler's theorem on homogeneous functions}
The partial derivatives of the Dupire equation~\cite{Gatheral2006} are with respect to the strike price $K$. Thus to derive a Dupire-like PIDE, we will require partial derivatives in terms of $x'$ (the analogous variable for $K$). This can be done by invoking Euler's theorem for homogeneous functions~\cite[pp. 317]{Kishan2007} to $v$ and we get
	\begin{equation*}
		x\fr{\pr v}{\pr x} + x'\fr{\pr v}{\pr x'} = v,
	\end{equation*}
since $v$ has been shown to be homogeneous in $x$ and $x'$ of degree one. By differentiating the above equation with respect to $x$ and $x'$, we obtain
	\begin{equation*}
		x\fr{\pr^2 v}{\pr x^2} = -x'\fr{\pr^2 v}{\pr x \pr x'}, \quad x'\fr{\pr^2 v}{\pr x'^2} = -x\fr{\pr^2 v}{\pr x' \pr x},
	\end{equation*}
respectively. Hence it follows that
	\begin{equation*}
		x^2\fr{\pr^2 v}{\pr x^2} = x'^2\fr{\pr^2 v}{\pr x'^2}.
	\end{equation*}
The only term left to account for is the integral in (\ref{eqn:PIDE}). Notice that the first integrand term depends on~$y$; we want to transfer the dependency on $y$ to the third argument (i.e., $x'$). This can be achieved by the homogeneity property in (\ref{eqn:homogen}), and we obtain
	\begin{align*}
		v(xy,t; x') &= v\left(xy,t;\fr{x'y}{y}\right) = yv\left( x,t;\fr{x'}{y} \right).
	\end{align*}
Thus, setting $u(x',t; x) = v(x,t; x')$ and replacing all the $x$ derivatives with $x'$ derivatives and substituting the above rearrangement for the integrand, we get
	\begin{align}
		\label{eqn:DupireLike}
		\begin{split}
		\fr{\pr u}{\pr t} &- (q(t) + \kappa\lambda)u - (r(t) - q(t) - \kappa\lambda)x'\fr{\pr u}{\pr x'} + \fr{1}{2}\sigma(t)^2x'^2\fr{\pr^2 u}{\pr x'^2} \\
		& {} + \lambda \int_0^\infty \left( yu\left( \fr{x'}{y},t; x \right) - u(x',t; x) \right)f(y) \, \d y = 0
		\end{split}
	\end{align}
with
	\begin{equation}
		\label{eqn:DupireCond}
		u(x',T; x) = \phi(x';x),
	\end{equation}
since $u$ now depends on the variables $x'$ and $t$ with $x$ as a parameter. Equations~(\ref{eqn:DupireLike}) and (\ref{eqn:DupireCond}) together form the Dupire-like PIDE system for options in a jump-diffusion framework. Note that this reduces to the standard Dupire PDE as seen in \cite{Gatheral2006} in the absence of jumps (i.e., $\lambda = 0$) when $\phi$ is either the call or put payoff.

### 2017-12-11 UOW_thesis_template_v2-0/thesis_template/chapters/jumpdiffAmer.tex
:art: Changes from December 8
:art: More changes from Monday 11 Dec

    and at $x = S^*(t)$, the following smooth pasting conditions are assumed to be satisfied:

@@

		Similar to how we dealt with $I_{3,a}$, we interchange the order of integration between $y$ and $z$, declare a substitution of $p = (zy)/S^*(u)$, then reverse the integration between $p$ and $y$. The result of these steps is

@@

        	First, we let the triple integral in~\eqref{eqn:amerJumpPut} be $I$. Then using the expression for $g_c$ from~\eqref{eqn:g} gives
        	\begin{align*}
        		I &= rK \int_t^T\int_0^\infty\int_{S^*(u)}^\infty\fr{1}{w}\J(w,t,u)\fr{1}{z}\K_\lambda\left( \fr{x}{zw},t,u \right) \, \d z \, \d w \, \d u \\
        		& {} \quad - q \int_t^T\int_0^\infty\int_{S^*(u)}^\infty\fr{1}{w}\J(w,t,u)\K_\lambda\left( \fr{x}{zw},t,u \right) \, \d z \, \d w \, \d u \\
        		& {} \quad + \int_t^T\int_0^\infty\int_{S^*(u)}^\infty \fr{1}{w}\J(w,t,u)\fr{1}{z}\K_\lambda\left( \fr{z}{w},t,u \right) \\
        		&{} \quad \quad \times  \lambda \int_{0}^{S^*(u)/z} \left( v_{\text{a}}^{\text{call}}(zy,t) - (zy-K) \right)f(y) \, \d y \, \d z \, \d w \, \d u \\
        		& = I_1 + I_2 + I_3,
        	\end{align*}
        	where the order of integration between $z$ and $w$ had to be swapped in order to simplify the Heaviside function in $g_c$. We first look at $I_1$ and incorporate eq.~\eqref{eqn:jump11} for $\J$ and the first identity for $\K_\lambda$ in~\eqref{eqn:shiftKernel} to arrive at
        	        		\begin{align*}
        			I_1 &= rK\int_t^T \fr{e^{(r+\lambda)(u-t)}}{\sigma\sqrt{u-t}} \int_0^\infty\int_{S^*(u)}^\infty \fr{1}{w} \delta(w-1) \fr{1}{z} N'\left( z_{2\lambda}\left( \fr{x}{zw}, t, u \right) \right) \, \d z \, \d w \, \d u \\
        			& {}\quad rK\int_t^T \fr{e^{(r+\lambda)(u-t)}}{\sigma\sqrt{u-t}} \ds\sum\limits_{n=1}^{\infty} \fr{(\lambda(u-t))^n}{n!\sqrt{n\sigma_Y^2}}\int_0^\infty \int_{S^*(u)}^\infty \fr{1}{zw}N'\left( \fr{\log w + n\mu_Y}{\sqrt{n\sigma_Y^2}} \right) \\
        			& {} \quad \quad \times N'\left( z_{2\lambda}\left( \fr{x}{zw}, t, u \right) \right) \, \d z \, \d w \, \d u \\
        			&= I_{1,a} + I_{1,b},
        		\end{align*}
        		where we assumed $r$, $q$, and $\sigma$ are constants. Now for $I_{1,a}$, the limits of integration for $z$ and $w$ are constants with respect to each other. So we will swap them and then use $f(a) = \int_0^\infty \delta(x-a) f(x) \, \d x$ for $a > 0$ to obtain
        		$$
        			I_{1,a} = rK\int_t^T \fr{e^{(r+\lambda)(u-t)}}{\sigma\sqrt{u-t}}\int_{S^*(u)}^\infty \fr{1}{z} N'\left( z_{2\lambda}\left( \fr{x}{z}, t, u \right) \right) \, \d z \, \d u.
        		$$
		Making use of Lemma~\ref{lem:2a} and checking the full form of $z_{2\lambda}$ in~\eqref{eqn:z2lambda} allows us to set
			$$
				a = S^*(u), \enskip b = \infty, \enskip a_1 = \fr{1}{\sqrt{n\sigma_Y^2 + \sigma^2(u-t)}}, \enskip
			b_1 = z_2\left( \fr{x}{z}, t, u \right),
			$$
		to give
			\begin{align*}
				I_{1,a} &=  rK\int_t^T e^{(r+\lambda)(u-t)}N\left(z_{2\lambda}\left( \fr{x}{S^*(u)},t,u\right) \right) \, \d u.
			\end{align*}
		We cannot proceed to simplify this as the integral with respect to $u$ cannot be computed without knowing $S^*$ for all of $u$ from $t$ to $T$.

>>>>

    and at $x = S^*(t)$, \textcolor{blue}{the following smooth pasting conditions are assumed to be satisfied}:

@@

		\textcolor{blue}{Similarly to how we dealt with $I_{3,a}$}, we interchange the order of integration between $y$ and $z$, declare a substitution of $p = (zy)/S^*(u)$, then reverse the integration between $p$ and $y$. The result of these steps is

@@

        	First, we let the triple integral in~\eqref{eqn:amerJumpPut} be $I$. Then using the expression for $g_c$ from~\eqref{eqn:g} gives
        	\begin{align*}
        		I &= rK \int_t^T\int_0^\infty\int_{S^*(u)}^\infty\fr{1}{w}\J(w,t,u)\fr{1}{z}\K_\lambda\left( \fr{x}{zw},t,u \right) \, \d z \, \d w \, \d u \\
        		& {} \quad - q \int_t^T\int_0^\infty\int_{S^*(u)}^\infty\fr{1}{w}\J(w,t,u)\K_\lambda\left( \fr{x}{zw},t,u \right) \, \d z \, \d w \, \d u \\
        		& {} \quad + \int_t^T\int_0^\infty\int_{S^*(u)}^\infty \fr{1}{w}\J(w,t,u)\fr{1}{z}\K_\lambda\left( \fr{z}{w},t,u \right) \\
        		&{} \quad \quad \times  \lambda \int_{0}^{S^*(u)/z} \left( v_{\text{a}}^{\text{call}}(zy,t) - (zy-K) \right)f(y) \, \d y \, \d z \, \d w \, \d u \\
        		& = I_1 + I_2 + I_3,
        	\end{align*}
        	where the order of integration between $z$ and $w$ had to be swapped in order to simplify the Heaviside function in $g_c$. We first look at $I_1$ and incorporate Eq.~\eqref{eqn:jump11} for $\J$ and the first identity for $\K_\lambda$ in~\eqref{eqn:shiftKernel} to arrive at
        	        		\begin{align*}
        			I_1 &= rK\int_t^T \fr{e^{(r+\lambda)(u-t)}}{\sigma\sqrt{u-t}} \int_0^\infty\int_{S^*(u)}^\infty \fr{1}{w} \delta(w-1) \fr{1}{z} N'\left( z_{2\lambda}\left( \fr{x}{zw}, t, u \right) \right) \, \d z \, \d w \, \d u \\
        			& {}\quad rK\int_t^T \fr{e^{(r+\lambda)(u-t)}}{\sigma\sqrt{u-t}} \ds\sum\limits_{n=1}^{\infty} \fr{(\lambda(u-t))^n}{n!\sqrt{n\sigma_Y^2}}\int_0^\infty \int_{S^*(u)}^\infty \fr{1}{zw}N'\left( \fr{\log w + n\mu_Y}{\sqrt{n\sigma_Y^2}} \right) \\
        			& {} \quad \quad \times N'\left( z_{2\lambda}\left( \fr{x}{zw}, t, u \right) \right) \, \d z \, \d w \, \d u \\
        			&= I_{1,a} + I_{1,b},
        		\end{align*}
        		where we assumed $r$, $q$, and $\sigma$ are constants. Now for $I_{1,a}$, the limits of integration for $z$ and $w$ are constants with respect to each other. So we will swap them and then use $f(a) = \int_0^\infty \delta(x-a) f(x) \, \d x$ for $a > 0$ to obtain
        		$$
        			I_{1,a} = rK\int_t^T \fr{e^{(r+\lambda)(u-t)}}{\sigma\sqrt{u-t}}\int_{S^*(u)}^\infty \fr{1}{z} N'\left( z_{2\lambda}\left( \fr{x}{z}, t, u \right) \right) \, \d z \, \d u.
        		$$
		Making use of Lemma~\ref{lem:2a} and checking the full form of $z_{2\lambda}$ in~\eqref{eqn:z2lambda} allows us to set
			$$
				a = S^*(u), \enskip b = \infty, \enskip a_1 = \fr{1}{\sqrt{n\sigma_Y^2 + \sigma^2(u-t)}}, \enskip
			b_1 = z_2\left( \fr{x}{z}, t, u \right),
			$$
		to give
			\begin{align*}
				I_{1,a} &=  rK\int_t^T e^{(r+\lambda)(u-t)}N\left(z_{2\lambda}\left( \fr{x}{S^*(u)},t,u\right) \right) \, \d u.
			\end{align*}
		We cannot proceed to simplify this as the integral with respect to $u$ cannot be computed without knowing $S^*$ for all of $u$ from $t$ to $T$.

### 2017-12-11 UOW_thesis_template_v2-0/thesis_template/chapters/jumpdiffEuro.tex
:art: Working through Jeff's suggestions again
:art: More changes from Monday 11 Dec

Analogous to \cite{Merton1976} and \cite{Frontczak2013}, we want to solve the problem (\ref{eqn:PIDE}), (\ref{eqn:PIDEcondition}). First, we assume that the function $v_\text{e} = v_\text{e}(x,t)$ denotes the European option with an underlying that is described by jump-diffusion dynamics, and that is a solution to~(\ref{eqn:PIDE}), (\ref{eqn:PIDEcondition}). Applying the Mellin transform of $v_\text{e}$ with respect to $x$ to (\ref{eqn:PIDE}), \eqref{eqn:PIDEcondition}, we get

@@

As a short foreword, all derivations presented in this section are formal. To find $\J$, we can actually bypass the complex integral required for an inverse Mellin transform. From \eqref{eqn:JMellin}, we have

@@

where $I$ is an arbitrary interval with endpoints $a$ and $b > a$; the interval can be open, half-closed or closed. For example, a call option has payoff $\phi(x) = \max(x-K,0)$ which can be formulated as

@@

		\max(x-K,0) = x\1_{[K,\infty)}(x) - K\1_{[K,\infty)}(x),

@@

where $I$ is the interval $[K,\infty)$. So the expression would be

@@

There is also interest in finding an exact solution for Kou's double exponentially distributed jumps \cite{Kou2002, Kou2004} using \eqref{eqn:optionJump} and \eqref{eqn:jumpGeneral} since recent empirical studies (in particular, the tests performed in~\cite{Ramezani1998}) suggest a better model for the asset process involves the jumps following a double exponential distribution. In particular, it may be of interest to see whether or not a Mellin transform route would generate a more elegant and simple solution in lieu of Kou's original solution, which involves the computation of quite complicated $Hh$ functions (see \cite[pp. 691]{Abramowitz1972}). There is also the possibility to extend \eqref{eqn:optionJump} to price American options in jump-diffusion models, which will be examined in chapter 5 of this thesis.

>>>>

Analogous to \cite{Merton1976} and \cite{Frontczak2013}, we want to solve the problem (\ref{eqn:PIDE}), (\ref{eqn:PIDEcondition}). First, we assume that the function $v_\text{e} = v_\text{e}(x,t)$ denotes the European option with an underlying that is \textcolor{blue}{described by} jump-diffusion dynamics, and that is a solution to~(\ref{eqn:PIDE}), (\ref{eqn:PIDEcondition}). Applying the Mellin transform of $v_\text{e}$ with respect to $x$ to (\ref{eqn:PIDE}), \eqref{eqn:PIDEcondition}, we get

@@

\textcolor{blue}{As a short foreword, all derivations presented in this section are formal. Moreover, we will be assuming that the random variable $Y$ could belong to any family of distributions where $\E[Y]$ is finite and that $\E[Y^{-\xi}]$ is convergent.} To find $\J$, we can actually bypass the complex integral required for an inverse Mellin transform. From \eqref{eqn:JMellin}, we have

@@

\textcolor{blue}{where $I$ is an arbitrary interval with endpoints $a$ and $b > a$; the interval can be open, half-closed or closed.} For example, a call option has payoff $\phi(x) = \max(x-K,0)$ which can be formulated as

@@

		\max(x-K,0) = x\1_{[K,\infty)}(x) - K\1_{[K,\infty)}(x).

@@

So the expression would be

@@

There is also interest in finding an exact solution for Kou's double exponentially distributed jumps \cite{Kou2002, Kou2004} using \eqref{eqn:optionJump} and \eqref{eqn:jumpGeneral} since \textcolor{blue}{recent empirical studies (in particular, the tests performed in~\cite{Ramezani1998}) suggest a better model for the asset process involves the jumps following a double exponential distribution.} In particular, it may be of interest to see whether or not a Mellin transform route would generate a more elegant and simple solution in lieu of Kou's original solution, which involves the computation of quite complicated $Hh$ functions (see \cite[pp. 691]{Abramowitz1972}). There is also the possibility to extend \eqref{eqn:optionJump} to price American options in jump-diffusion models, which will be examined in chapter 5 of this thesis.
